---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# emetricsrsw

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/danicamiguel/emetricsrsw.svg?branch=master)](https://travis-ci.org/danicamiguel/emetricsrsw)
<!-- badges: end -->

The goal of `emetricsrsw` package is to support the exercises and examples from Chapter 5 of **Introduction to Econometrics** by James H. Stock and Mark W. Watson. Since this textbook was designed to assist learning in introductory econometrics courses, it's expected that users of the textbook will use statistical analysis software program STATA. However, given that STATA is not an open-source and free software (i.e. you must pay to obtain an operating license) this makes it inaccessible to those interested in learning econometrics from this textbook. `emetricsrsw` allows users to utilize some of the most commonly used STATA commands in R to perform statistical analysis - making it convenient and accessible for all readers of this textbook interested in learning econometrics without having to use STATA. It also takes some of the pressure off from those familiar with STATA commands but aren't as familiar with R's interface. Have fun!

## Installation

`emetricsrsw` is hosted on Github and can be installed by running the following: 
```{r, warning=FALSE, message=FALSE}
devtools::install_github("danicamiguel/emetricsrsw")
```

```{r}
library(emetricsrsw)
```

## Data

The California Standardized Testing and Reporting dataset contains data on test performance, school characteristics and student demographic backgrounds. All of these data were obtained from the [California Department of Education](http://www.cde.ca.gov). For more information about this dataset see the [Companion Website](https://wps.pearsoned.com/aw_stock_ie_3/178/45691/11696965.cw/index.html) for Stock and Watson's Introduction to Econometrics. 

`dist_code`: District Code

`read_scr`: Average Reading Score

`math_scr`: Average Math Score

`county`: Country 

`district`: District

`gr_span`: Grade Span of District

`enrl_tot`: Total Enrollment

`teachers`: Teachers

`computer`: Number of Computers

`testscr` : Average Test Scores, (read_scr + math_scre)/2

`comp_stu`: Computers per Student (computer / enrl_tot)

`expn_stu`: Expentitures per Student (in $'s)

`str`: Student Teacher ratio (enrl_tot / teachers)

`el_pct`: Student Techer ratio (enrl_tot / teachers)

`meal_pct`: Percent Qualifying for Reduced-Price Lunch 

`calw_pct`: Percent Qualifying for Calworks

`avginc`: District Average Income (in $1000's)

## Example

```{r example}
library(emetricsrsw)
library(mosaic)

#using command to get list of summary statistics for a variable based on user input, also known as 'sum' in STATA
sum(mtcars)

<<<<<<< HEAD
sum_var(mtcars$mpg, mtcars)
=======
#sum_var(mtcars$mpg)
>>>>>>> d55eb0c7247119e72ef0761712db977a1d4bdd27
```


